Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
Burned section 5.
Fixed minor things.

\vincent{Should we introduce Koszul duality here and say what it does on quivers?}

@@

\begin{convention}
\textbf{All throughout the paper, all dissections are considered cellular.}
The case of non-cellular dissections will be discussed in Section~\ref{sec:nonCellularDissections}.
\end{convention}

@@

\section{Representation-theoretic interpretation}

\subsection{$\dissection$-accordions and string modules}

\subsection{$\dissection\dual$-slaloms and minimal projective presentations}

>>>>

@@

\begin{convention}
\textbf{All throughout the paper, all dissections are considered cellular.}
\end{convention}

@@
